LDATS Rodents Example

### 2020-03-18 doc/rodents-example.Rmd
vignette rebuilds
more tidying

This vignette walks through an example of **LDATS** at the command line and
was constructed using **LDATS** version `r vers` on `r today`.

@@

The `document_term_table` is a matrix of species (term) counts by sampling period (document). Importantly, the `document_term_table` contains raw counts of individual rodent captures, not catch per unit effort. The LDA models operate on proportions and weight the information from each sampling period according to total catch (document size). Similarly, the TS models use the LDA compositional breakdown and weight the information from each period according to the total catch. We therefore give both models un-adjusted data. The values in the `document_term_table` must be integers.

@@

```{r lda set not quiet}
lda_model_set2 <- LDA_set(document_term_table = rodents$document_term_table,
                         topics = c(2:3),
                         nseeds = 2)
```

@@

```{r load lda model set, include = F}
load(here::here('vignettes', 'rodents-example-files', 'lda_model_set.Rds'))
rm(lda_model_set2)
```

@@

```{r reload ts, include = F}
load(here::here('vignettes', 'rodents-example-files', 'changepoint_models.Rds'))
```

@@

```{r load ldats results, include = F}
load(here::here('vignettes', 'rodents-example-files', 'lda_ts_results.Rds'))
```

>>>>

This vignette walks through an example of **`LDATS`** at the command line and
was constructed using **`LDATS`** version `r vers` on `r today`.

@@

The `document_term_table` is a matrix of species (term) counts by sampling period (document). Importantly, the `document_term_table` contains raw counts of individual rodent captures, not catch per unit effort. The LDA models operate on proportions and weight the information from each sampling period according to total catch (document size). Similarly, the TS models use the LDA compositional breakdown and weight the information from each period according to the total catch. We therefore give both models unadjusted data. The values in the `document_term_table` must be integers.

@@

```{r lda set not quiet, eval =F}
lda_model_set2 <- LDA_set(document_term_table = rodents$document_term_table,
                         topics = c(2:3),
                         nseeds = 2)
```

@@

```{r load lda model set, include = F}
load(file.path('.', 'rodents-example-files', 'lda_model_set.Rds'))
rm(lda_model_set2)
```

@@

```{r reload ts, include = F}
load(file.path('.', 'rodents-example-files', 'changepoint_models.Rds'))
```

@@

```{r load ldats results, include = F}
load(file.path('.', 'rodents-example-files', 'lda_ts_results.Rds'))
```
